Blueprint

### 2020-11-24 blueprint.tex
Updates blueprint

\title{Blueprint}
\author{}
\date{\today}
\maketitle

@@

Let $R$ be a commutative ring.

@@

\begin{definition}[zero divisor]
	Two elements $x$ and $y$ of $R$ are zero divisors if $x \neq 0$, $y \neq 0$ and $x y = 0$.
\end{definition}

\begin{definition}[entire ring]
	The ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
\end{definition}

@@

@@

%\begin{definition}[localization of a ring]

%\end{definition}

%\begin{definition}[spectrum of a ring]

%\end{definition}

>>>>

\title{Blueprint}
\author{Anthony Bordg}
\date{\today}
\maketitle

@@

\begin{definition}[zero divisor]
	Two elements $x$ and $y$ of a ring are zero divisors if $x \neq 0$, $y \neq 0$ and $x y = 0$.
\end{definition}

\begin{definition}[entire ring]
	A ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
\end{definition}

Let $R$ be an entire ring.

@@

@@

\begin{remark}
	If $\mathfrak{p}$ is a prime ideal, then $1 \notin \mathfrak{p}$.
\end{remark}

\begin{ex}
	Let $\mathfrak{p}$ be a prime ideal and $S$ be the complement of $\mathfrak{p}$ in $R$. Prove $S$ is a multiplicative submonoid of $R$. 
\end{ex}

@@

\begin{cons}
	Let $S$ be a multiplicative submonoid of $R$. We consider pairs $(r, s)$ with $r \in R$ and $s \in S$ and we define the following relation on them
	\[
	(r, s) \sim (r', s')
	\]
	if and only if there exists $s_1 \in S$ such that $s_1(s' r - s r') = 0$. One checks that the relation $\sim$ is an equivalence relation. The equivalence class of a pair $(r, s)$ is denoted by $r/s$ and the set of equivalence classes is denoted by $S^{-1} R$. We define the following addition on $S^{-1} R$.
	\[
	\frac{r}{s} + \frac{r'}{s'} = \frac{r s' + r' s}{s s'}
	\]
	We also define the following multiplication on $S^{-1} R$. 
	\[
	\frac{r}{s} \times \frac{r'}{s'} = \frac{r r'}{s s'}
	\]
\end{cons}

\begin{ex}
	Prove $(S^{-1} R, 0/1, +, 1/1, \times)$ is a ring.
\end{ex}

\begin{definition}[quotient ring]
	Let $S$ be a multiplicative submonoid of $R$. The quotient ring of $R$ by $S$ is $S^{-1} R$. 
\end{definition}

\begin{definition}[local ring]
Let $\mathfrak{p}$ be a prime ideal of $R$ and $S$ the complement of $\mathfrak{p}$ in $R$. The local ring of $R$ at $\mathfrak{p}$, denoted $R_{\mathfrak{p}}$, is $S^{-1} R$. 	
\end{definition}

\begin{cons}
	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}(U)$ to be the set of all functions 
	\[
	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
	\]
	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$.  
\end{cons}

\begin{ex}
	Prove $\mathscr{O}$ is a sheaf of rings on Spec $R$. 
\end{ex}

\begin{definition}[spectrum of a ring]
	The spectrum of the ring $R$ is the pair consisting of the topological space $Spec R$ together with the sheaf of rings $\mathscr{O}$.
\end{definition}
